Matching Bullets

### 2015-12-10 imaging-paper.Rnw
Start on smoothing factor variation, much more coming

\begin{figure}[hbtp]
  \centering
<<circlefits, echo=FALSE, fig.width=7, fig.height=7, out.width='\\linewidth', warning=FALSE>>=
qplot(y, resid, data=subset(db2, x == 100), #colour=factor(x), 
      geom="line", size=I(.75), colour=I("grey70")) + 
  facet_wrap(~part, ncol=2) + scale_colour_brewer(palette="Paired") +
  theme_bw() + theme(legend.position="bottom") + 
  geom_line(aes(y, resid, group = x), colour="black", size=.75, alpha=0.5,
             data = filter(db1, part==5, x == 100)[,c("y", "resid", "x")]) +
  ylab("Residuals from circular fit") +
  ggtitle("Bullet 1-5 in black")
@
\caption{Circle fit for each cross section of bullet 2, with bullet 1-5 overlaid.\label{fig:circlefits} \hh{Bullet 1-5 matches best with the first land of the second bullet.}}%
\end{figure}

@@

\subsection{Varying smoothing factor}
\hh{XXX it would be good to have a discussion of the smoothing factor XXX}

>>>>

\begin{figure}[hbtp]
  \centering
<<circlefits, echo=FALSE, fig.width=7, fig.height=7, out.width='\\linewidth', warning=FALSE>>=
qplot(y, resid, data=subset(db2, x == 100), #colour=factor(x), 
      geom="line", size=I(.75), colour=I("grey70")) + 
  facet_wrap(~part, ncol=2) + scale_colour_brewer(palette="Paired") +
  theme_bw() + theme(legend.position="bottom") + 
  geom_line(aes(y, resid, group = x), colour="black", size=.75, alpha=0.5,
             data = filter(db1, part==5, x == 100)[,c("y", "resid", "x")]) +
  ylab("Residuals from circular fit") +
  ggtitle("Bullet 1-5 in black")
@
\caption{Circle fit for each cross section of bullet 2, with bullet 1-5 overlaid.\label{fig:circlefits} Bullet 1-5 matches best with the bullet 2-1}
\end{figure}

@@

\subsection{Varying smoothing factor}
As mentioned, the algorithm for peak/valley detection depends on the selection of a smoothing window, called the smoothing factor. In particular, for detecting and removing the grooves prior to fitting a Loess regression, we selected a smoothing factor of 35
